Open source symbolic multibody dynamics software

### 2012-02-21 PetersonGedeHubbard2012.tex
Fixed stupid error I made in maths

\begin{align}
    A\prime &\triangleq \tilde{M}^{-1} \tilde{A} \\
    B\prime &\triangleq \tilde{M}^{-1} \tilde{B}
\end{align}

Now we will have matrices $A\prime$ and $B\prime$ which are of size $(o +
n) \times (o - m + n - l)$ and $(o + n) \times p)$. We need to now extract only
the rows which are associated with the independent quantities. We will call the
new matrices reduced matrices $A$ and $B$ and compute them with the following

\begin{align}
    P \prime &\triangleq \begin{matrix}
        P_{qi} & \bm{O}_{(n - l) \times (o - m)} \\
        \bm{O}_{(o - m) \times (n - l)} & P_{ui}
    \end{matrix} \\
    A &\triangleq P\prime^T A\prime \\
    B &\triangleq P\prime^T B\prime \\
\end{align}

>>>>

\begin{align}
    A^\prime &\triangleq \tilde{M}^{-1} \tilde{A} \\
    B^\prime &\triangleq \tilde{M}^{-1} \tilde{B}
\end{align}

Now we will have matrices $A^\prime$ and $B^\prime$ which are of size $(o +
n) \times (o - m + n - l)$ and $(o + n) \times p)$. We need to now extract only
the rows which are associated with the independent quantities. We will call the
new reduced matrices $A$ and $B$ and compute them with the following

\begin{align}
    P^\prime &\triangleq \begin{bmatrix}
        P_{qi} & \bm{O}_{(n - l) \times (o - m)} \\
        \bm{O}_{(o - m) \times (n - l)} & P_{ui}
    \end{bmatrix} \\
    A &\triangleq P^{\prime T} A^\prime \\
    B &\triangleq P^{\prime T} B^\prime \\
\end{align}
